---
title: "Test Re-Test ICC Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

Here we import the relevant Packages to our project 

```{r,warning=FALSE,message=FALSE}
library(ggsci)
library(cowplot)
library(ggthemes)
library(ggridges)
library(philentropy)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(psych)
library(ICC)
library(lattice)
library(lpSolve)
library(irr)
library(plot.matrix)
library(reshape)
library(plotly)
library(tidyverse)
library(svglite)
```

Now we need to Import the Data (Gradient 1, 2 and 3 of all the Subjects)
```{r}
g1g2g3 = read.csv('G1G2G3AVG_results.csv')
g1g2g3$YeoNets = factor(g1g2g3$YeoNets, levels = c('VN','SMN','DAN','SN','LN','FPN','DMN'))
head(g1g2g3)

```

Data of Gradient 1

```{r}
g1 = read.csv('G1_results.csv')
DMN_SMN_G1 = g1 %>% filter(YeoNets == 'DMN' | YeoNets == 'SMN' )
DMN_SMN_G1$YeoNets = factor(DMN_SMN_G1$YeoNets, levels = c('DMN','SMN'))

head(DMN_SMN_G1)
```


Plot of the Yeo Networks

```{r}
data = g1g2g3 %>% filter(YeoNets != 'LN')
data$YeoNets = factor(data$YeoNets, levels = c('DMN','FPN','SN','DAN','SMN','VN'))

p2 <- ggplot(data, aes(x = Gradient1, y = YeoNets, color = YeoNets, fill = YeoNets)) +
  geom_density_ridges(alpha = 0.6, scale = 3) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_discrete(expand = c(0,0)) +
  scale_fill_manual(values = c('#CD3E4E','#E69422', '#BE3AFA', '#00760E', '#4682B4', '#781286')) +
  scale_color_manual(values = c('#CD3E4E','#E69422', '#BE3AFA', '#00760E', '#4682B4', '#781286')) +
  coord_cartesian(clip = 'off') +
  labs(y='', title='YeoNets') + theme_ridges() + 
  theme(legend.position = 'none',
        plot.title = element_text(face='bold', size=20, hjust=0.5))

p2
```

Now we plot for each sub only the DMN and SMN Networks

```{r}
data = DMN_SMN_G1%>% select(-c(YeoNets,Yeo))
drops<- c("YeoNets","Yeo")
data= DMN_SMN_G1[,!(names(DMN_SMN_G1) %in% drops)]

p3<-ggplot(DMN_SMN_G1, aes(x= sub.1, color=YeoNets, fill = YeoNets)) +
  geom_density(alpha=0.4)+
  scale_x_continuous(limits = c(min(data%>%select(-X)),max(data%>%select(-X))))+
  scale_y_continuous(limits = c(0, 40))+
  labs(x="sub1 ses2",y='', title='YeoNets') + theme_ridges() + 
  theme(legend.position = 'none',
        plot.title = element_text(face='bold', size=10, hjust=0.5))

p3
```

Compute the ICC values of the DMN_SMN vector between each Subject 

```{r}
#split the data sessions 
ses1_df<- DMN_SMN_G1[,2:10]
ses2_df<- DMN_SMN_G1[,11:19]
iccMatrix<- matrix(ncol=ncol(ses1_df), nrow=ncol(ses2_df))



for(i in 1:ncol(ses1_df)){
  
  for(j in 1:ncol(ses2_df)){
  
    targetVec<- ses1_df[ ,i]
    otherVec<- ses2_df[,j]
    combinVec<-cbind(targetVec,otherVec)
    v<-icc(combinVec, model = "twoway", type = "agreement", unit = "single")$value
    iccMatrix[i,j]<-v
    
  }##end for j
  
  
}##end for i


matrix_df<- as.data.frame(iccMatrix)
colnames(matrix_df)<-c('Sub1','Sub2','Sub3','Sub4','Sub5','Sub6','Sub7','Sub8','Sub9')
rownames(matrix_df)<-c('Sub1','Sub2','Sub3','Sub4','Sub5','Sub6','Sub7','Sub8','Sub9')
y<- colnames(matrix_df)
x<- rownames(matrix_df)
y<-rep(y, times = 9)
dft<-t(combinVec)
df <- melt(matrix_df)
pMatrix<-ggplot(data =df , aes(x=variable, y=y,fill= value)) + 
  geom_tile()+
  labs(x="ses1",y='ses2', title='ICC') +
  theme(plot.title = element_text(face='bold', size=10, hjust=0.5),axis.text.x = element_text(size=8, angle = 45, hjust = 1),axis.text.y = element_text(size=8,angle = 45, hjust = 1) )

pMatrix
ggsave(file="pmatrixSingle.png", pMatrix, width=6, height=5, dpi=400)
ggplotly(pMatrix)

```


ks_test value 

```{r}

DMN = DMN_SMN_G1 %>% filter(YeoNets == 'DMN')
SMN = DMN_SMN_G1 %>% filter(YeoNets == 'SMN')  
#Preper the data
DMN_ses1<- DMN[,2:10]
SMN_ses1<- SMN[,2:10]
DMN_ses2<- DMN[,11:19]
SMN_ses2<- SMN[,11:19]
ks_test_Matrix<- matrix(ncol=2, nrow=ncol(ses2_df))

head(DMN_ses1)
```

computing the ks_test value 

```{r,warning=FALSE,message=FALSE}

for(i in 1:2){
  
  for(j in 1:ncol(ses2_df)){
    
    targetVec<- eval(parse(text = paste0("DMN_ses",i)))[ ,j]
    otherVec<- eval(parse(text = paste0("SMN_ses",i)))[ ,j]
    v<- ks.test(targetVec,otherVec)$stat
    ks_test_Matrix[j,i]<-v
    
  }##end for j
  
  
}##end for i

```

The results

```{r}
ks_test_Matrix<-as.data.frame(ks_test_Matrix)
ks_test_Matrix$diff<-(ks_test_Matrix$V1-ks_test_Matrix$V2)
colnames(ks_test_Matrix)<-c("ses1","ses2","diff")
ks_test_Matrix
```


Compute th ICC value between the two ses Ks_test values 

unit parameter = Average
```{r}
icc(ks_test_Matrix[ , c("ses1","ses2")], model = "twoway", type = "agreement", unit = "average")

```

unit parameter = Single

```{r}
icc(ks_test_Matrix[ , c("ses1","ses2")], model = "twoway", type = "agreement", unit = "single")
```

